Arrows for Parallel Computations

### 2017-11-27 paper/content/bestAndWorstBenchmarks.tex

>>>>

}

%\bestAndWorstBenchmarks

\newcommand{\meanOverhead}{
\begin{table}[]
\centering
\label{tab:meanOverhead}
\captionsetup[subtable]{justification=centering}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest 1000}\label{sudokuMeanFactor-1000}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-16000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest 16000}\label{sudokuMeanFactor-16000}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\caption{\rmtest 11213 32}\label{sm-rmMeanFactor-11213-32}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest 11213 64}\label{sm-rmMeanFactor-11213-64}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\caption{\torustest (dist) 4096}\label{torusMeanFactor-4096}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest (dist) 44497 256}\label{dist-rmMeanFactor-44497}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-4253.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\jacobitest (dist) 4253}\label{jacobiMeanFactor-4253}
\end{subtable}
\caption{Overhead in the benchmarks}
\end{table}
}

\meanOverhead
